\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2017-04-15 article.tex
Editor update from 2/16/17
Editor code indentation corrections

Most of these plotting tools were developed by building upon the \pkg{ggplot2} package (\citealt{ggplot2}). As such, most of these plotting tools can be customized by appending syntax from the \pkg{ggplot2} package, as will be demonstrated in example code throughout this paper. Moreover, some of these plotting tools have interactive capabilities that were developed with the use of the \pkg{plotly} package (\citealt{plotly}) (see Subsection \ref{interaction}).

@@

\begin{Code}
R> pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal, "devYear")
R> plotPath(pathBZ, sbGeneal, "devYear", fontFace = 2) + ggplot2::xlab
+    ("Development Year")
\end{Code}

@@

\begin{Code}
R> sbFilt <- sbGeneal[complete.cases(sbGeneal[1:3]),]
R> sbFiltIG <- dfToIG(sbFilt)
R> pathCL <- getPath("Clark", "Lawrence", sbFiltIG, sbFilt, "yield")
R> plotPath(pathCL, sbFilt, "yield") + ggplot2::xlab("Yield")
R> pathCL2 <- getPath("Clark", "Lawrence", sbFiltIG, sbFilt, "devYear")
R> plotPath(pathCL2, sbFilt, "devYear", "yield") + ggplot2::xlab("Development
+    Year") + ggplot2::ylab("Yield")
\end{Code}

@@

\begin{Code}
R> plotPathOnAll(pathTN, sbGeneal, sbIG, "devYear", bin = 3, pathEdgeCol =
+    "red", nodeSize = 2.5, pathNodeSize = 4) + ggplot2::theme(axis.text =
+    ggplot2::element_text(size = 12), axis.title = ggplot2::element_text(size
+    = 12))
\end{Code}

@@

\begin{Code}
R> plotPathOnAll(pathTN, sbGeneal, sbIG, "devYear", bin = 6, pathEdgeCol =
+    "seagreen2", nodeSize = 1, pathNodeSize = 3) + ggplot2::xlab("Development
+    Year")
\end{Code}

@@

\begin{Code}
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", bin = 3, pathEdgeCol =
+    "purple") + ggplot2::xlab("Yield")
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", "devYear", pathEdgeCol =
+    "orange") + ggplot2::xlab("Yield") + ggplot2::ylab("Development Year")
\end{Code}

@@

\begin{Code}
>R varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow",
+    "Pella", "Tokyo", "Young", "Zane")
>R plotDegMatrix(varieties, sbIG, sbGeneal) + ggplot2::scale_fill_continuous
+    (low = "white", high = "darkgreen") + ggplot2::theme(legend.title =
+    ggplot2::element_text(size = 15), legend.text = ggplot2::element_text
+    (size = 15)) + ggplot2::labs(x = "Variety", y = "Variety")
\end{Code}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> statIG <- dfToIG(statGeneal)
R> pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal,
+    "gradYear", isDirected = FALSE)
R> plotPath(pathCB, statGeneal, "gradYear", fontFace = 4) + ggplot2::xlab
+    ("Graduation Year") + ggplot2::theme(axis.text = ggplot2::element_text
+    (size = 10), axis.title = ggplot2::element_text(size = 10)) +
+    ggplot2::scale_x_continuous(expand = c(.1, .2))
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200) +
+    ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title =
+    ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous
+    (expand = c(.1, .2)) + ggplot2::xlab("Graduation Year")
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200, nodeSize =
+    .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray") +
+    ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title =
+    ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous
+    (expand = c(.1, .2)) + ggplot2::xlab("Graduation Year")
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200, nodeSize =
+    .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray",
+    animate = TRUE)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{Code}
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", pathEdgeCol = "orange",
+    animate = TRUE)
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", "devYear", pathEdgeCol =
+    "orange", animate = TRUE)
\end{Code}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> desDC <- getDescendants("David Cox", statGeneal, 15)
R> tableDC <- table(statGeneal[match(desDC$label, statGeneal$child), ]$school)
R> tail(sort(tableDC), 5)
\end{CodeInput}
\begin{CodeOutput}
          The Johns Hopkins University 
                                     9 
Universidade Federal do Rio de Janeiro 
                                    17 
       North Carolina State University 
                                    18 
             Universidade de São Paulo 
                                    28 
                  University of London 
                                    35
\end{CodeOutput}
\end{CodeChunk}

>>>>

Most of these plotting tools were developed by building upon the \pkg{ggplot2} package (\citealt{ggplot2}). As such, most of these plotting tools can be customized by appending syntax from the \pkg{ggplot2} package, as will be demonstrated in example code throughout this paper. Moreover, some of these plotting tools have interactive capabilities that were developed with the use of the \pkg{plotly} package (\citealt{plotly}) (see Section \ref{interaction}).

@@

\begin{Code}
R> pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal, "devYear")
R> plotPath(pathBZ, sbGeneal, "devYear", fontFace = 2) +
+    ggplot2::xlab("Development Year")
\end{Code}

@@

\begin{Code}
R> sbFilt <- sbGeneal[complete.cases(sbGeneal[1:3]),]
R> sbFiltIG <- dfToIG(sbFilt)
R> pathCL <- getPath("Clark", "Lawrence", sbFiltIG, sbFilt, "yield")
R> plotPath(pathCL, sbFilt, "yield") + ggplot2::xlab("Yield")
R> pathCL2 <- getPath("Clark", "Lawrence", sbFiltIG, sbFilt, "devYear")
R> plotPath(pathCL2, sbFilt, "devYear", "yield") +
+    ggplot2::xlab("Development Year") + ggplot2::ylab("Yield")
\end{Code}

@@

\begin{Code}
R> plotPathOnAll(pathTN, sbGeneal, sbIG, "devYear", bin = 3, pathEdgeCol =
+    "red", nodeSize = 2.5, pathNodeSize = 4) +
+    ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
+    axis.title = ggplot2::element_text(size = 12))
\end{Code}

@@

\begin{Code}
R> plotPathOnAll(pathTN, sbGeneal, sbIG, "devYear", bin = 6, pathEdgeCol =
+    "seagreen2", nodeSize = 1, pathNodeSize = 3) +
+    ggplot2::xlab("Development Year")
\end{Code}

@@

\begin{Code}
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", bin = 3, pathEdgeCol =
+    "purple") + ggplot2::xlab("Yield")
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", "devYear",
+    pathEdgeCol = "orange") + ggplot2::xlab("Yield") +
+    ggplot2::ylab("Development Year")
\end{Code}

@@

\begin{Code}
>R varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow",
+    "Pella", "Tokyo", "Young", "Zane")
>R plotDegMatrix(varieties, sbIG, sbGeneal) +
+    ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") +
+    ggplot2::theme(legend.title = ggplot2::element_text(size = 15),
+    legend.text = ggplot2::element_text(size = 15)) +
+    ggplot2::labs(x = "Variety", y = "Variety")
\end{Code}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> statIG <- dfToIG(statGeneal)
R> pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal,
+    "gradYear", isDirected = FALSE)
R> plotPath(pathCB, statGeneal, "gradYear", fontFace = 4) +
+    ggplot2::xlab("Graduation Year") + ggplot2::theme(axis.text =
+    ggplot2::element_text(size = 10), axis.title =
+    ggplot2::element_text(size = 10)) +
+    ggplot2::scale_x_continuous(expand = c(.1, .2))
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200) +
+    ggplot2::theme(axis.text = ggplot2::element_text(size = 8),
+    axis.title = ggplot2::element_text(size = 8)) +
+    ggplot2::scale_x_continuous(expand = c(.1, .2)) +
+    ggplot2::xlab("Graduation Year")
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200,
+    nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol =
+    "lightgray") + ggplot2::theme(axis.text = ggplot2::element_text(size = +    8), axis.title = ggplot2::element_text(size = 8)) +
+    ggplot2::scale_x_continuous(expand = c(.1, .2)) +
+    ggplot2::xlab("Graduation Year")
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200,
+    nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol =
+    "lightgray", animate = TRUE)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{Code}
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", pathEdgeCol = "orange",
+    animate = TRUE)
R> plotPathOnAll(pathCL, sbFilt, sbFiltIG, "yield", "devYear",
+    pathEdgeCol = "orange", animate = TRUE)
\end{Code}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> desDC <- getDescendants("David Cox", statGeneal, 15)
R> tableDC <- table(statGeneal[match(desDC$label,
+    statGeneal$child), ]$school)
R> tail(sort(tableDC), 5)
\end{CodeInput}
\begin{CodeOutput}
          The Johns Hopkins University
                                     9
Universidade Federal do Rio de Janeiro
                                    17
       North Carolina State University
                                    18
             Universidade de São Paulo
                                    28
                  University of London
                                    35
\end{CodeOutput}
\end{CodeChunk}
